Predicting Kamala Harris's Victory in the 2024 US Election

### 2024-11-01 paper/paper.qmd
Update estimand part.

## Estimand

@@

## Model Summary
```{r}
#| echo: false
#| tbl-cap: Complete Model Coefficient Summary Table
#| warning: false
#| message: false
# Get summary of the regression model
model_summary <- summary(regression_model)

# Extract and convert the coefficients summary to a data frame
coefficients_df <- as.data.frame(model_summary$coefficients)

# Set column names for coefficients_df
colnames(coefficients_df) <- c("Estimate", "Std. Error", "t value")[1:ncol(coefficients_df)]

@@

# Create a data frame for additional statistics with consistent column names and rounded to 2 decimals
additional_stats <- data.frame(
  Estimate = round(c(r_squared, adj_r_squared, f_statistic, residual_se), 2),
  `Std. Error` = NA,
  `t value` = NA,
  row.names = c("R-squared", "Adjusted R-squared", "F-statistic", "Residual Std. Error")
)

# Ensure column names are identical between data frames
additional_stats <- additional_stats[, colnames(coefficients_df), drop = FALSE]

# Load dplyr
library(dplyr)

@@

# Display the full summary table using kable
library(knitr)
kable(full_summary_df)
```

>>>>

## Estimand
In this analysis, the estimand is the true effect of polling factors on the projected support for Trump and Harris in the 2024 U.S. election. Specifically, this effect encompasses how variables like poll quality, transparency, sample size, and timing influence predicted vote percentages for Kamala Harris and Donald Trump across states. This build-up of estimand ensures consistency by clarifying that our target effect is the overall impact of these factors on candidates’ state-by-state electoral prospects. The estimand guides the model design and interpretation to achieve our goal of predicting the election outcome.

@@

## Model Summary
```{r}
#| echo: false
#| tbl-cap: Complete Model Coefficient Summary Table
#| warning: false
#| message: false

# Get summary of the regression model
model_summary <- summary(regression_model)

# Extract and convert the coefficients summary to a data frame
coefficients_df <- as.data.frame(model_summary$coefficients)
colnames(coefficients_df) <- c("Estimate", "Std. Error", "t value", "Pr(>|t|)")

@@

# Create a data frame for additional statistics with consistent column names and rounded to 2 decimals
additional_stats <- data.frame(
  Estimate = round(c(r_squared, adj_r_squared, f_statistic, p_value, residual_se), 2),
  `Std. Error` = NA,
  `t value` = NA,
  `Pr(>|t|)` = NA,
  row.names = c("R-squared", "Adjusted R-squared", "F-statistic", "F-statistic p-value", "Residual Std. Error")
)

# Ensure column names are identical between data frames
colnames(additional_stats) <- colnames(coefficients_df)

@@

# Display the full summary table using kable
kable(full_summary_df[!rownames(full_summary_df) %in% "F-statistic p-value", c("Estimate", "Std. Error", "t value")])
```
